OR Multi Disturbance

### 2023-01-06 OR_original_model.Rmd
old code: OR postprocessing

## grab matching data
obs.pre  = Yw[,t04-1]
obs.dist = Yw[,t04]
obs.tlo  = Yw[,tlo]
obs.class= dextract[,"t2004"]/10
```

@@

}
dev.off()
```

@@

>>>>

## grab matching data
obs.pre  = Yw[,t04-1]
obs.dist = Yw[,t04]
obs.tlo  = Yw[,tlo]
obs.class= dextract[,"t2004"]/10

save(elist,obs.pre,obs.dist,obs.tlo,obs.class,file="elist.RData")
```

@@

}
dev.off()
save(stats,file="stats.RData")
```

@@

## preprocess timeseries example for visualization
```{r}
## visualization to help select a site to look at
plotly::plot_ly(data.frame(obs.pre=obs.pre,obs.post=obs.dist),x=~obs.pre,y=~obs.post)
which.min((obs.pre-13.3)^2+(obs.dist-5.1)^2) ## select a point

## settings
site = 188
exp.name = "P1Q1R4" #"P1Q1R1"  ## manually run for each experiment **

## data
NT = 33
Yi = matrix(NA,NT,3)  ## observed data
Yi[1:ncol(Yw),3] = Yw[site,]  ## only Cw observed

## model
load(paste0("OR_SD_",site,"_",exp.name,".RData"),envir = viz)
pool.names=c("Cleaf","Csoil","Cstem")
test = viz$test

for(i in 1:3){

  plot(Yi[,i],
       ylim = range(rbind(CI.Na,Yi[,i],CI.D),na.rm=TRUE),
       type='n',
       ylab=pool.names[i],xlab="time")
  ecoforecastR::ciEnvelope(1:ncol(CI.Nf),CI.Nf[1,],CI.Nf[3,],col=ecoforecastR::col.alpha("blue",0.5))
  ecoforecastR::ciEnvelope(1:ncol(CI.Na),CI.Na[1,],CI.Na[5,],col=ecoforecastR::col.alpha('#b2df8a',0.7))
  lines(CI.Na[3,],col="#b2df8a",lwd=2)
  points(Yi[,i])
  lines(CI.D[3,])

}
save(Yi,CI.Na,CI.D,file=paste0("OR_TS_",site,"_",exp.name,".RData"))
```

## summary info for filter divergence figures
```{r}
exp.name = "P1Q1R4" #"P1Q1R1"

for(i in seq_along(exps)){

}
```
